Evaluating infectious disease forecasts with allocation scoring rules

### 2023-04-25 alloscore_manuscript/allocation.rmd
two very small but potentially crucial additions

High level points to cover in introduction:
\begin{itemize}
\item People are using infectious disease forecasts as an input to decision making
\item There are standard ways to evaluate forecasts that are responsive to decision making context, and use of those methods is relatively common in other fields like economics and meteorology
\item However, there's not much work in infectious disease that does this
\item In practice, infectious disease forecasts have typically been evaluated with "off the shelf" scoring rules such as the WIS which is an approximation to CRPS, log score, and so on.
\item In this work, our goal is to begin to address that gap. We focus on a resource allocation setting.
\item There is past work focusing on resource allocation in the operations research literature, but it doesn't take the step of getting to a measure of forecast skill.
\end{itemize}

>>>>

High level points to cover in introduction:
\begin{itemize}
\item People are using infectious disease forecasts as an input to decision making
\item There are standard ways to evaluate forecasts that are responsive to decision making context, and use of those methods is relatively common in other fields like economics and meteorology
\item However, there's not much work in infectious disease that does this
\item In practice, infectious disease forecasts have typically been evaluated with "off the shelf" scoring rules such as the WIS which is an approximation to CRPS, log score, and so on.
\item In this work, our goal is to begin to address that gap. We focus on a resource allocation setting.
\item There is past work focusing on resource allocation in the operations research literature, but it doesn't take the step of getting to a measure of forecast skill.
\item That is, while there is plenty of work on 
\begin{itemize}
\item DM under risk, where probabilities are taken as known and expected utility is maximized
\item DM under uncertainty, where probabilities are taken as unknown and robust (i.e. maximin) decisions are sought
\end{itemize}
little seems to have been said on how forecasts can be evaluated by how well they convert a problem of DM under uncertainty to a problem of DM under risk.
\end{itemize}
